TrueGrid: Code the Table, Tabulate the Data

### 2016-06-17 true-grid/paper_SEMS16.tex
Related work

>>>>

\section{Related Work}

This work is positioned at the intersection of end-user programming and professional software development~\cite{EUSE}. The particular link between software engineering and spreadsheet has been explored before. For instance, Cunha et al. present model-based programming environments for spreadsheets~\cite{cunha2014model}.
The focus of this work is to improve reliability of spreadsheet engineering by applying model-driven techniques. 
In this work we primarily focus on improving programmer experience.

Integrating spreadsheet-based user interfaces with code editors is a simple form of a heterogeneous programming environment (e.g.,~\cite{schrage2008beyond}), originally pioneered in the work on structure editors, and recently popularized by the Jetbrains Meta Programming System~\cite{MPS}. Although this kind of work aims for a much more invasive integration, it is in line with the goal of having best user interfaces for each aspect of the code. A similar strand of research is explored in the context of DSLs by Adam and Schultz~\cite{adam2015towards}.
